\documentclass[a4paper]{article}

\usepackage{tabu}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage[left=1.6in,right=1.6in,top=1.3in,bottom=1.2in]{geometry}
\usepackage{titlesec}
%\usepackage[none]{hyphenat}

\newcommand{\fillrule}{\leaders\hbox{\rule{1pt}{1pt}}\hfill\hspace{0pt}}

\setlength{\parskip}{0in}
\setlength\parindent{0in} %indent and add lines between paras

\pagenumbering{gobble}

\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\begin{document}
	\begin{center}
		\setlength{\parskip}{\baselineskip}
		{\Huge Tailoring Horror Games with Biometrics}
		
		{\LARGE AI Search for Relaxing Music}
	\end{center}

	\begin{center}
		\textbf{The participant must read and complete both pages}
		
		\textbf{Ask the researcher about anything you don't understand}
	\end{center}
	
	\section{Experiment}
	
	You are invited to participate in a research study exploring how biometric sensors can be integrated into horror games. The aim of this experiment is to determine whether a system which scares the user based on their measured reaction to previous scares is better than one which scares the user at random. During the session, you will wear a sensor on your fingers to measure your body's stress response. You will be shown the controls to a computer game, then be given 10 minutes to explore a haunted house, searching for items. After the experiment is complete you will be asked to complete a very short survey about whether you enjoyed the game.
	
	\section{Risks}
	
	There are no direct risks to you by participating in this study. If you have heart problems, or have had bad reactions to horror games/films in the past, you may not participate in the study. If you are concerned about the jump-scare, alert the researcher now and you can be shown an example of a jump-scare (it's not very scary). This will not impact your participation in the study. You are free to stop at any point during the study, without reason.
	
	\section{Time Cost}
	
	Your total time involved will be approximately 20 minutes, with 10 minutes of that time spent playing the game. You are under no obligation to participate in anything after this session.
	
	\section{Confidentiality}
	
	You will not be personally identifiable as having participated in this research. Any personally identifiable information will be deleted after the project's completion. Any information released will be linked solely to your Candidate ID and not your name. No individual raw data from the session will be released, unless you sign the Voluntary Release of Data. Sensor readings (including jump-scare metadata) in aggregate (averages, sums, and trends across all participants), will be published in the finished paper but will not be included in a data dump unless you sign the release.

	\section{Contacts}
	
	To receive the results of this project once it is complete, you may sign up to the mailing list at \url{http://eepurl.com/dKBEHc}. Participants must sign the \emph{Voluntary Release of Data} and remember their unique participant ID if they wish to identify their results. The expected completion date is June 2019.\\
	
	If you have questions or concerns about this study, please contact:\\
	
	\begin{tabu}{lX[c]r}
		\textbf{Steven Lowes} & steven.lowes@durham.ac.uk & Researcher\\
		\textbf{Magnus Bordewich} & magnus.bordewich@durham.ac.uk & Supervisor\\
	\end{tabu}

	\newpage
	
	\begin{center}
		\setlength{\parskip}{\baselineskip}
		{\Huge Consent Form}
		
		{\LARGE Tailoring Horror Games with Biometrics}
	\end{center}

	\textbf{Participant ID:} \fillrule\\
	
	The researcher I have spoken to is \fillrule
	
	\begin{center}
		\textbf{Please confirm the following by ticking the boxes and signing below}
		
		\textbf{Alert the researcher if any are not true}
	\end{center}
	
	\begin{tabu}{Xr}
		I have had an opportunity to ask questions and discuss the study & $\square$\\\\
		I have received satisfactory answers to all of my questions & $\square$\\\\
		I have received enough information about the study & $\square$\\\\
		I understand that I am free to withdraw from the study at any time
		and without having to give a reason for withdrawing & $\square$\\\\
		I have read the procedure described above and I voluntarily agree to participate in this study and have received a copy of this description & $\square$\\\\
	\end{tabu}\vspace{0.5cm}

	Signed \fillrule \vspace{0.5cm}
	
	Date \fillrule \vspace{0.5cm}
	
	Name (Block Capitals) \fillrule \vspace{0.5cm}
	

	\begin{center}
		\textbf{--- This section is optional ---}
	\end{center}
	
	\section{Voluntary Release of Data}
	\begin{center}		
		\textbf{To agree, tick the boxes and sign below}
	\end{center}

	\begin{tabu}{Xr}
		I understand that I am not obligated to complete this part of the consent form and it will in no way impact my participation in the study & $\square$\\\\
		I grant the researchers permission to release into the public domain: anonymised data collected during this session, consisting of my participant ID, Sensor Measurement, Song Lists, Answers to Questions, and metadata (such as during which song a measurement was taken) & $\square$\\\\
		I understand that my name and any personally-identifiable information will be kept strictly confidential & $\square$\\\\
	\end{tabu}\vspace{0.5cm}

	Signed \fillrule \vspace{0.5cm}
	
	Date \fillrule \vspace{0.5cm}
	
	Name (Block Capitals) \fillrule
\end{document}